
%TODO add members
\section{Team members}
%from rules:  Main involved research areas in the team work
Currently, the team has eight active members - three bachelor's, two masters and three PhD students in the second year of their studies. All team members are students in the School of Computer Science, University of Birmingham. The overview of team members follows along with a description of their background and research interests. The final team line-up is likely to change before the competition as more members will contribute.

\subsection{Lenka Mudrova}

She is a PhD student with research interests in AI planning and scheduling. In the team, she has two roles. First, she is the team leader, which mainly includes representation of the team when formal communication outside of the team is necessary. Also, she makes sure that every member of the team knows what is happening, how their modules will be used within the system and what is required from them. The second role is that she is working also on the robot's subsystem. Her research interest in Artificial Intelligence (AI) planning will be useful for creating the robot's overall behaviour next year. Moreover, she is interested in computer vision and speech recognition.

\subsubsection*{Scientific background}
She did her bachelor's and master's studies at the Czech Technical University in Prague with a focus on Robotics. This study branch gave her a wide range of knowledge in the fields of mechatronics and artificial intelligence. She was involved as a team leader of the student robotics team FELaaCZech that took part in the international competition Eurobot for four years. 

Currently, she is a PhD student with a focus on AI planning and scheduling, which are important techniques for a robot to make decisions on when, how and what needs to be performed. Such decisions are necessary in service robotics when a robot needs to complete tasks assigned by a human. The robot needs to have a control framework that makes decisions concerning which particular task should be executed. The quality of the decisions influence the overall performance of the robot and of course, the robot's goal must satisfy as many of the requirements assigned by the humans as possible. Requirements for the robot's control framework are deadline awareness, handling uncertainty about task duration and resources, creating plans on how to complete general tasks and awareness of changes in the environment where the robot operates. 

Her research is part of the EU STRANDS project \cite{strands}. "STRANDS aims to enable a robot to achieve robust and intelligent behaviour in human environments through adaptation to, and the exploitation of, long-term experience (at least 120 days by the end of the project).". Therefore, the robot's control framework will exploit long-term experiences and observations of the robot's world. 

\subsection{Marco Antonio Becerra Pedraza}

He is a PhD student in the School of Computer Science, University of Birmingham. His research interests are 3D perception, human sensing, knowledge representation and reasoning. Inside the team he has worked with the human sensing capabilities of the robot.

\subsubsection*{Scientific background}
He obtained his bachelor degree in Mechatronics Engineering from the Instituto Polit\'{e}cnico Nacional in Mexico and a master degree in Computer Science from the Universidad Nacional Aut\'{o}noma de M\'{e}xico. He is a former member of the PUMAS RoboCup@Home team.

During his PhD, he will be doing research about semantic mapping of human events. The topic has two main components:

Semantic mapping can be conceived as an extension of the mapping problem \cite{Nuchter08_TowardsSemanticMaps}. Traditionally maps were used in robotics mostly for navigation purposes. But the environment has additional spatial information that needs to be handled. Semantic maps extend the concept of maps to handle more features from the environment (e.g. structure, functionalities, events). The goal is to reason about the scene (e.g. planning, prediction, explanation, interpretation).

Activity recognition is about using observations from the world to build representations of the ongoing actions. Later, these representations can be used to find associated structures.

\subsection{Manolis Chiou}

He is a PhD student with a multidisciplinary background in control engineering, robotics and AI. His work on BARC involves but is not limited to control, navigation, localisation and in the future Human-Robot-Interaction (HRI).

\subsubsection*{Scientific background}

His first degree is in Control Engineering from the Technological Institute of Piraeus, in which he got involved in a variety of robotic projects including demonstrating these projects to the public and exhibitions. His undergraduate thesis was on implementing control algorithms to robots (e.g. Model Predictive Control for stability/balance). He has an MSc in Computational Intelligence with his master thesis on formation control and transportation of objects with a swarm of robots.  

The working title of his PhD thesis is ``Flexible robotic control via co-operation between an Operator and an AI based control system". It addresses the problem of variable autonomy in teleoperated mobile robots. Variable autonomy refers to the different levels of autonomous capabilities that are implemented on a robot.

Robots used on demanding and safety critical tasks (e.g. search and rescue, hazardous environments inspection, bomb disposal), which are currently teleoperated, could soon start to benefit from autonomous capabilities. Such capabilities include algorithms for automatic robot navigation, algorithms for Simultaneous Localisation And Mapping (SLAM) and etc. Robots could usefully use AI control algorithms to autonomously take control of certain functions when the human operator is suffering a high workload, high cognitive load, anxiety, or other distractions and stresses. In contrast, some circumstances may still necessitate direct human control of the robot. The research will tackle the problem by designing control algorithms for switching between the different autonomy levels in an optimal way. 


\subsection{Sean Bastable}

He is a Computer Science bachelor's student in his final year. It is expected that he will continue to further his studies with a master's degree in Robotics. As the oldest BARC member, he has solid experience with ROS and different robotic platforms. He is also one of the team members who attended RoCKIn camp 2014 in Rome.

\subsubsection*{Scientific background}
 
His final year project was about investigating and implementing a visual localisation system for a mobile robot. This allowed the robot to continue localising in environments where laser based localisation cannot be used. A good example of this is in domestic environments where the presence of people moving around the robot may obstruct the laser scan and provide false readings.
 
The project used a ceiling facing omnidirectional camera on the top of a robot in order to take pictures of its surroundings.
The robot was trained by taking many pictures of the environment, along with location data provided through laser based localisation under ideal conditions. When localising, it can take additional pictures and compare them to the training images in order to find an estimate of its location. Principal Component Analysis (PCA) was used to match images in the localisation phase to those in the test phase. 

Another potential use of this project is to provide an initial location estimate to a laser based localisation system in order to allow the robot to quickly localise from any position without any human input.

This project follows on his previous summer project of a drinks serving robot used in a launch event for the 2014 British Science Festival. As the robot was moving in a crowd, one of the key failure points was that it could become de-localised. The robot had the need to know exactly where it is in order to effectively navigate through gaps in-between crowds. Visual localisation was considered as a potential solution but due to time constrains was not implemented.